---
title: "npillana_Assignment 1"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Loading Libraries

```{r}

library(dplyr)
library(ISLR)
library(ggplot2)

```

# Data Preparation
##Loading DataSet

```{r}
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc") 
summary(SafeBabies)

```

## Clean the data. Check for any missing vales 


```{r}

table(is.na(SafeBabies))
sum(is.na(SafeBabies))

```



# Divide data based on shelveLoc i.e, Good, Bad and Medium

```{r}

Good <- filter(SafeBabies, ShelveLoc == "Good")
Bad <- filter(SafeBabies, ShelveLoc == "Bad")
Medium <- filter(SafeBabies, ShelveLoc == "Medium")

```

# Visualizing the Price and Sales based on Shelve location

```{r}

ggplot(data=SafeBabies) + aes(x = ShelveLoc, y = Price) + geom_boxplot(fill = "blue") + labs(x = "ShelveLoc", title = "Price based on ShelveLoc") + theme_minimal()
ggplot(data=SafeBabies) + aes(x = ShelveLoc, y = Sales) + geom_boxplot(fill = "blue") + labs(x = "ShelveLoc", title = "Sales based on ShelveLoc") + theme_minimal()
ggplot(data=SafeBabies) + aes(x = Price, y = Sales) + geom_point(size = 1L, colour = "blue") + labs(title = "Sales based on Price") + theme_minimal()

```

Based on above visuals the ShelveLoc with Good has the highest sales when compared to others and the price for Good ShelveLoc is slightly higher than Bad and Medium

# Build a Linear Model

### Lets build a linear model to predict the sales for all ShelveLoc 

```{r}

Good_Shelve <- lm(Sales ~ Price, data = Good)
Bad_Shelve <- lm(Sales ~ Price, data = Bad)
summary(Good_Shelve)
summary(Bad_Shelve)

```
The adjusted R2 tells you the percentage of variation explained by only the independent variables that actually affect the dependent variable.
Adjusted R-squared:0.43 for Good ShelveLoc and Adjusted R-squared:0.3032 for Bad ShelveLoc, which explains variability in the car price for Car Seats.

# Formulating the Problem
Total Profit= Sales * Profit_per_Unit 
Profit_per_Unit= price – cost
Sales=b1*price+b0
Total Profit= (price – cost) *(b1*price+b0)  =b1*price^2+b0*price-cost*b1*price-cost*b0
                                             =b1*price^2+(b0 -cost*b1)*price-cost*b0

Now we have to find the optimal value, set the derivative to Zero
Total Profit derivative = 2b1*price + b0-b1*cost

Then Price is;
Price = (-b0)-(b1*cost))/2b1

# Solving the Problem

```{r}

#Lets calculate optimal price for car seat for both Good and Bad Shelve at cost $55

OptimalPrice <- function(prod_cost, b_0, b_1) {return(((-1 * b_0) + (b_1 * prod_cost)) /(2 * b_1))}
Good_OptimalPrice<- OptimalPrice(55, Good_Shelve$coefficients[1], Good_Shelve$coefficients[2])
Good_OptimalPrice
paste("optimal price for car seats with good shelve",Good_OptimalPrice)

Bad_OptimalPrice<- OptimalPrice(55, Bad_Shelve$coefficients[1], Bad_Shelve$coefficients[2])
Bad_OptimalPrice
paste("optimal price for car seats with Bad shelve",Bad_OptimalPrice)

```

### Calculate the optimal prive when the cost varies from $40 to $80 with $5 increments

```{r}

Varied_Cost <- seq(40,85, by=5)

for( i in Varied_Cost){
  OptimalPrice_Good <- OptimalPrice(Varied_Cost, Good_Shelve$coefficients[1],Good_Shelve$coefficients[2])
  OptimalPrice_Bad <- OptimalPrice(Varied_Cost, Bad_Shelve$coefficients[1],Bad_Shelve$coefficients[2])
}


```

# Now, we will combine production costs and optimal prices for good and bad shelve location

```{r}

Combine_cost <- data.frame(cbind(Varied_Cost,OptimalPrice_Good, OptimalPrice_Bad))
Combine_cost

```

# Visualizing the optimal cost with varying with Production costs from $40 to $85 for Good Shelve and Bad Shelve 

```{r}

ggplot(data=Combine_cost) + aes(x = Varied_Cost, y = OptimalPrice_Good) + geom_boxplot(fill = "blue") + labs(x = "Varied_Cost", title = "Optimal Price for Good shelve") + theme_minimal()
ggplot(data=Combine_cost) + aes(x = Varied_Cost, y = OptimalPrice_Bad) + geom_boxplot(fill = "blue") + labs(x = "Varied_Cost", title = "Optimal Price for Bad shelve") + theme_minimal()


```

# The above Visuals show that the Optimal Price for the Car seats at Good Shelve is higher than the Optimal Price for the Car seats at Bad Shelve.


